\chapter{Code of Conduct}

We are committed to making BornHack an inclusive and welcoming event for
everyone. The most important rule is: \b{Be excellent to eachother}.

Sadly, technology events have a notorious reputation for harassment. We've set
these ground rules to make it abundantly clear that this kind of behaviour is
not acceptable, so that everyone can feel comfortable attending BornHack.

Everyone who visits BornHack is required to abide by this code of conduct, both
at the event and on any online channels. We will not tolerate harassment of
participants or discriminatory behaviour of any form. Specifically:

\begin{itemize}
    \item
    Do not engage in homophobic, racist, transphobic, ableist, sexist, or
    otherwise prejudiced behaviour.

    \item
    Do not harass people. Stalking, unconsented physical contact, or unwanted
    sexual attention is harassment.

    Dressing or acting in a certain way is not consent.

    \item
    BornHack is a shared space, but every participant's personal space is their
    own. If you are asked to leave someone alone, or to leave a village, you
    must respect this.

    \item
    Some attendees may not want to be filmed or photographed. Respect their
    wishes.

    \item
    Aggression and elitism are not welcome - nobody should be afraid to ask
    questions.
\end{itemize}

BornHack takes place in an area with beautiful nature all around. We expect
everyone to treat the venue with the utmost care and respect. We will not
tolerate any kind of vandalism against nature, this includes littering. We are
guests in nature, and everyone is expected to act as such.

If you break these rules, we may expel you from the event without a refund, and
we may ban you from future BornHack events.

If you are being harassed or witness a breach of this code of conduct, you can
get in touch with us in the following ways:

\begin{itemize}
    \item
    Find a member of event staff and let them know. All our volunteer staff
    will be briefed on how to handle a harassment situation.

    \item
    Drop us an email at \mailto{conduct@bornhack.org}. If you prefer to speak
    to a female you can write to \mailto{sarah@bornhack.org}. If you prefer to
    speak to a male you can write to \mailto{vidir@bornhack.org}.

    \item
    Call the 24/7 duty officer on \b{(+45) 27 80 80 90}.
\end{itemize}

If you have any comments or queries, you can get in touch with our conduct team
at \mailto{conduct@bornhack.org}.

\i{This Code of Conduct is heavily based on (if not verbatim stolen from) our
friends at EMF}.

%% vim: set ft=tex tw=80 :
